Random Forests", OAs

### 2023-11-14 src/oa_RF.Rmd
oa.rf

df <- df %>% drop_na() %>% 
  group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(oa11cd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("oa11cd" = "oa11cd"))

>>>>

df <- df %>% #drop_na() %>% 
  group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(oa11cd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("oa11cd" = "oa11cd"))
